---
title: "Basic Operations in R"
output: html_notebook
---

_Problems adapted from the PSDS textbook_

## Calling built-in functions

Create a variable `my_name` that contains your name

```{r}

```


Create a variable `name_length` that holds how many letters (including spaces) are in your name (use the `nchar()` function)

```{r}

```



Print the number of letters in your name

```{r}

```

Create a variable `now_doing` that is your name followed by "is programming!" (use the `paste()` function)

```{r}

```

Make the `now_doing` variable upper case

```{r}

```


## Operations with Numbers

Pick two of your favorite numbers (between 1 and 100) and assign them to variables `fav_1` and `fav_2`

```{r}


```


Divide each number by the square root of 201 and save the new value in the original variable

```{r}


```


Create a variable `raw_sum` that is the sum of the two variables. Use the `sum()` function for practice.

```{r}

```


Create a variable `round_sum` that is the `raw_sum` rounded to 1 decimal place. Use the `round()` function.

```{r}

```


Create two new variables `round_1` and `round_2` that are your `fav_1` and `fav_2` variables rounded to 1 decimal places

```{r}

```

Create a variable `sum_round` that is the sum of the rounded values

```{r}

```


Which is bigger, `round_sum` or `sum_round`? (You can use the `max()` function!)

```{r}
max(sum_round, round_sum)
```


## Functions and Conditionals

Define a function `is_twice_as_long` that takes in two character strings, and returns whether or not (e.g., a boolean) the length of one argument is greater than or equal to twice the length of the other.
_Hint_: compare the length difference to the length of the smaller string


```{r}



```

Call your `is_twice_as_long` function by passing it different length strings to confirm that it works. Make sure to check when _either_ argument is twice
as long, as well as when neither are!

```{r}


```

Define a function `describe_difference` that takes in two strings. The function should return one of the following sentences as appropriate 

- "Your first string is longer by N characters"

- "Your second string is longer by N characters"

- "Your strings are the same length!"

```{r}
describe_difference <- function(first, second) {
  diff <- nchar(first) - nchar(second)
  if (diff > 0) {
    sentence <- paste("Your first string is longer by", diff, "characters")
  } else if (diff < 0) {
    sentence <- paste("Your second string is longer by", -diff, "characters")
  } else {
    sentence <- "Your strings are the same length!"
  }
  sentence # return the sentence
} 

```



Call your `describe_difference` function by passing it different length strings to confirm that it works. Make sure to check all 3 conditions

```{r}
describe_difference( "dog", "elephant")

```


